---
title: "Introduction to StatComp21090"
author: "Bessie"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to StatComp21090}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Overview

__StatComp21090__ is a simple Construct functions to calculate European/Amrican call/put option price by diffrence method(\code{Eoption} and \code{Aoption}). 

I will use _Eoption_ and _Aoption_ to varify the Option parity formula, and show that the American call option's price is equal to the European.


## Option parity formula

We just show the european option parity formula
$$c_t+Ke^{-r(T-t)} = p_t+S_t$$
So at the initial moment(t=0), we have
$$c_0+Ke^{-rT}=p_0+S_t$$
we choose T=30, sigma=0.1, S0=1, r=0.1, q=0.1, K=0.2:0.2:2
```{r,eval=FALSE}
a <- numeric(10)
b <- numeric(10)
for (i in 1:10) {
  a[i] <- Eoption(30,0.1,1,0.1,0.1,0.2*i,"c")+0.2*i*exp(-0.1*30)
  b[i] <- Eoption(30,0.1,1,0.1,0.1,0.2*i,"p")+1
}
plot(a,col="red")
par(new = TRUE)
plot(b,type = "l",col="blue")
```

obviously the euqality holds.

## compare American call option and European call option

we choose T=30, sigma=0.1, S0=1, r=0.1, q=0.1, K=0.2:2

```{r,eval=FALSE}
c <- numeric(10)
d <- numeric(10)
for (i in 1:10) {
  c[i] <- Eoption(30,0.1,1,0.1,0.1,0.2*i,"c")
  d[i] <- Aoption(30,0.1,1,0.1,0.1,0.2*i,"c")
}
plot(c,col="red")
par(new = TRUE)
plot(d,type = "l",col="green")
```
they are equal.